### 2018-07-05 Paper/Rebuttal/rebuttal.tex

Where possible, key modifications have been highlighted in blue in the revised
manuscript.

We hope that with these modifications
the paper is found suitable for publication in the {\it International Journal of Heat and Mass Transfer}.

\clearpage

\section*{Referee 1}
\begin{enumerate}[leftmargin=*,itemsep=24pt]
\item \textbf{It is worth having some detailed on NEMD for example, what thermostats were used, 
numbers of atoms, and length of simulations etc.}

This suggestion has been incorporated in the revised manuscript.

\item \textbf{The readers would appreciate if the authors add original potential equation for SW (rather than
showing Table 2 without having equation)$?$}

This suggestion has been incorporated in the revised manuscript.

\item \textbf{It is recommended to justify (or discuss) why the authors chose the specific numbers of sample.
Also, the system size is very critical to calculate the thermal conductivity using NEMD, and it is
worth justifying the choice of system size for NEMD.}

As suggested by the referee, we have justified the choice of the number of samples in the revised manuscript.
Regarding the choice of system size, we have emphasized in the revised manuscript that the focus of this
work is on demonstrating an efficient methodology for quantifying the uncertainties in NEMD predictions
within a limited computational budget. The considered range for system size is found to be sufficient for
this purpose.

\section*{Referee 2}
\begin{enumerate}[leftmargin=*,itemsep=24pt]
\item \textbf{The range of parameters considered in the study is quite limited (L: five values in the range of 50a ~ 100a; dT/dz: five values in the range of 1.5/a ~ 2.5/a). Since both L and dT/dz vary by at most a factor of two, the subsequent analyses and the conclusions drawn based on the analyses could be biased. For a more thorough uncertainty quantification study, a larger sample size is likely needed, and the parameters would need be varied by larger extents. For L, one possible reference is the effective phonon mean path. For dT/dz, a lower bound could be some value larger than the noise level of MD simulations.}

We would like to emphasize that the focus of this work is on demonstrating a methodology for quantifying the
uncertainty in NEMD predictions. Specifically, in the initial part, we develop efficient response surfaces
to capture the relationship between simulation inputs: length, temperature gradient and the discrepancy in
bulk thermal conductivity predictions. Note that we do not aim to enhance the accuracy of NEMD predictions.
Moreover, the proposed methodology accounts for limitated availability of computational resources. The
consider range of system size is found to be suitable for this purpose. In order to avoid MD noise, we
have used average temperature at the bin point during the data production NVE ensemble. Hence, the
impact of noise on NEMD predictions in the considered range for $\frac{dT}{dz}$ is found to be negligible.

The above points have been emphasized in the revised manuscript. A justification for the choice of 5 points
along $L$ and $\frac{dT}{dz}$ has also been included.

\item \textbf{The authors mentioned in a few places the fluctuations in the applied thermal gradient (e.g., Line 9 from the bottom on Page 4). This is not very clear to the reviewer. Do the authors mean different applied thermal gradients? By the way, the term “thermal gradient” is typically referred to as “temperature gradient”. If the temperature gradient is evaluated in regions far away from the thermostats (e.g., around z = 0.5L in Fig. 2), would the thermostats affect the temperature gradients?}

Significant temperature fluctuations are observed especially in the vicinity of the thermostats in our setup
as shown in Figure 2. As a result, it is possible that the temperature gradient experienced by the
system is different from that specified in the input. Hence, the applied temperature gradient is also considered
to be a potential source of uncertainty in our analysis. We have attempted to clarify this in the revised
manuscript.

As suggested by the referee, ``thermal gradient" has been replaced with ``temperature gradient" in the 
revised manuscript.

The impact of thermostating on the temperature gradient is expect to decay with distance from the thermostats
as observed in Figure 2.

\item \textbf{For the NEMD simulations, what is the total simulation time? Another comment is about the system size in the width and height directions. Based on the reviewer’s experience, the NEMD calculated thermal conductivities are not very sensitive to the domain sizes in the width and height directions. Usually using a size around 5a for the width and height would be sufficient. This could be taken into account to reduce the simulation time.}

Simulation time has been included in the revised manuscript (Table 1) as suggested by the referee. As pointed
out by the referee, the impact of width and height was not found to be significantly large. 
As discussed in the manuscript, the choice of width and height in this study was an outcome of a careful
analysis aimed at minimizing temperature fluctuations during different stages in the NEMD simulation. As
suggested by the referee, a smaller width and height could have been used to further reduce computational
effort.

\item \textbf{For Si, previous results show that the phonon mean free path could span a wide range (e.g., from 10-2 to 103 um, see for example Fig. 11 of J. Comput. Theor. Nanosci. 5, 1–12, (2008)). When comparing the NEMD simulation domain size with the phonon mean free path, the authors should take this into account.}

We acknowledge the referee's input and are aware that thermal conductivity in NEMD is dependent on the 
dimension of simulation domain since phonons with longer mean free path can be ballistically transported.
Hence, the bulk thermal conductivity is estimated by extrapolating the relationship between the
inverse of conductivity and the inverse of system size as illustrated in Figure 5.

\item \textbf{When conducting the sensitivity analysis, the authors considered very small fluctuations ~O(10-5)*ni. Could the authors comment on the possible effects of larger fluctuations (e.g., 1$\%$ or 10$\%$)$?$}

We would like to clarify that small perturbations in the nominal estimates of the Stillinger-Weber (SW)
potential parameters are introduced to estimate the partial derivatives in Eq.8 with reasonable accuracy using
finite difference. In fact, the prior intervals for the SW parameters are considered to be $\pm 10\%$ for the
purpose of sensitivity analysis and constructing a reduced order surrogate as mentioned in section 5.

\item \textbf{Many of the results (e.g., Figs. 5 and 9) in the manuscript essentially show internal consistency. It would be helpful if the authors could check whether the results could be extended to cases outside the considered parameter ranges (i.e., to check the predictive power of the model analysis). The purpose of uncertainty quantification should be understanding what affects the uncertainty in the final results, so that people can actively control or accurately report the uncertainties. A predictive model would be more valuable to the fellow researchers.}

The referee makes an important point. However, we would like to point out that the overall objective of the
proposed methodology is calibration of the inter-atomic potential using a Bayesian framework. To
reduce computational effort, we construct efficient surrogates in Figures 5 and 9. Note that the accuracy
of the surrogates is tightly coupled with the choice of training points that essentially lie within the
considered intervals for length and the temperature gradient in one case and the SW potential parameters
in the other case. Hence, the surrogates can be reliably used only for the purpose of sensitivity analysis
and calibration in the considered input domain. A predictive model while certainty useful is beyond the
scope of this work. Additionally, verifying the accuracy of the surrogates outside the considered domain 
would involve large computational effort and is not expected to enhance the proposed methodology in this work.

\item \textbf{The reviewer would like to point out one relevant paper (IJHMT 112, 267-278 (2017)), which studies the uncertainty quantification of EMD predicted thermal conductivities.}

Suggested reference has been cited appropriately in the revised manuscript.

\item \textbf{In Eq. (1), the numerator should be q’’, meaning heat flux (W/m2).}

Referee's suggestion has been incorporated in the revised manuscript.

\item \textbf{The abbreviations (e.g., PC, DGSM) need only be explained in the first occurrence.}

This suggestion has been incorporated in the revised manusctript.

\item \textbf{In Fig. 5, it is worth checking whether the extrapolating L-1 to 0 will give the expected k for bulk Si.}

Figure 5 has been updated and the extrapolated bulk thermal conductivity estimates have been reported in the
revised manuscript.

### 2018-07-05 Paper/disc.tex
..

In this paper, we have attempted to identify and address some of the challenges
pertaining to uncertainty analysis of bulk thermal conductivity predictions 
using non-equilibrium molecular dynamics (NEMD) simulations. Specifically, we focused
on investigating the impact of system size, and variability in the applied thermal
gradient on predictions. In order to quantify the discrepancy between NEMD
predictions and experiments, response surfaces were  
constructed at bulk temperatures, $T$ = 300~K, 500~K, and 1000~K.  
It was found that the discrepancy is predominantly impacted by size while the 
effect of variability in the applied thermal gradient is negligible in the considered
interval. The response surface approach presented here relies on a small number of
MD runs and enables an accurate estimation of discrepancy at a given temperature
and a point in the 2D parameter space described by system-size and the applied
thermal gradient.

A possible enhancement of nominal SW parameter estimates for a given application
and the choice of material system is also highlighted in this work. To enable this,
we focus our efforts on understanding the sensitivity of predictions on individual potential
parameters. For this purpose, we estimate the so-called derivative based sensitivity
measures (DGSM) using random samples in the 7D parameter space. While individual
measures for the 7 parameters are not too distant from each other, the predictions
seem to be most sensitive towards $\gamma$. Sensitivity measures for $\alpha$,
$\lambda$, $q$, and $A$ are found to be comparable while those for $B$ and $p$
are relatively small.

A polynomial chaos surrogate model for the bulk thermal conductivity (observable)
as a function of SW potential
parameters at the bulk temperature of 300~K is constructed. The surrogate helps reduce the
computational effort required for forward propagation of the uncertainty from
parameters to the observable as well as for estimating the Sobol sensitivity indices.
Furthermore, the surrogate could be used to accelerate parameter calibration in a
Bayesian setting. However, since the surrogate relies on NEMD predictions, the
underlying computational effort is nevertheless significantly large. To circumvent
this challenge, we exploit our initial findings based on DGSM and construct
a reduced order surrogate in 5 dimensions by fixing the parameters, $B$ and $p$.
We verify its accuracy by estimating the relative
L-2 norm of the error between NEMD predictions in the full space and the reduced
order surrogate predictions, and comparing the probability distribution of the
bulk thermal conductivity in Figure~\ref{fig:verify}. Furthermore, our initial
sensitivity trends based on DGSM-analysis using 25 samples seem to agree favorably
with Sobol sensitivity analysis based on 10$^{6}$ samples. Hence, it can be said
that DGSM-based analysis with a few samples could offer huge computational gains
by reliably reducing the dimensionality of a surrogate for uncertainty analysis.

Finally, we highlight key aspects of parameter calibration in a Bayesian setting.
The underlying motivation stems from the fact that the nominal estimates of the SW
parameters did not consider measurement error, simulation noise, model form error,
and parametric uncertainties. Calibration in a Bayesian framework allows us to
incorporate such errors and uncertainties in an efficient manner and provides
a joint posterior distribution of the uncertain parameters. To minimize computational
costs pertaining to the calibration process, we suggest the following sequence of
steps: First, perform DGSM analysis to 
identify parameters that are not so important. Second, construct a reduced order
surrogate based on DGSM-analysis. Third, verify the accuracy of the surrogate
and compute Sobol indices. Fourth, consider only the important parameters in
calibration and construct a second surrogate in the reduced subspace. Fifth,
quantify the surrogate error to be accounted for during calibration. Sixth,
evaluate the joint posterior using an efficient MCMC-based algorithm.

In conclusion, the authors would like to highlight that the strategies presented 
in this work are not restricted to a Si bar and the Stillinger-Weber potential, and
could be extended to a wide range of applications and inter-atomic potentials for
the purpose of uncertainty analysis.

>>>>

In this paper, we have attempted to identify and address some of the challenges
pertaining to uncertainty quantification of bulk thermal conductivity predictions 
using non-equilibrium molecular dynamics (NEMD) simulations. Specifically, we focused
on investigating the impact of system size, and fluctuations in the applied temperature
gradient on predictions. In order to quantify the discrepancy between NEMD
predictions and experiments, response surfaces were  
constructed at bulk temperatures, $T$ = 300~K, 500~K, and 1000~K.  
It was found that the discrepancy is predominantly impacted by size while the 
effect of fluctuations in the applied temperature gradient is negligible in the considered
interval. The response surface approach presented here relies on a small number of
MD runs and enables an accurate estimation of discrepancy at a given temperature
and a point in the 2D parameter space described by system-size and the applied
temperature gradient.

A possible enhancement of nominal SW parameter estimates for a given application
and the choice of material system is also highlighted in this work. To enable this,
we focus our efforts on understanding the sensitivity of predictions on individual potential
parameters. In order to reduce the computational effort, we estimate the DGSMs
 and hence the upper bound
on Sobol\textquotesingle~total-effect sensitivity index using random samples in the 7D parameter space. 
While individual measures for the 7 parameters are not too distant from each other, the predictions
seem to be most sensitive towards $\gamma$. Sensitivity measures for $\alpha$,
$\lambda$, $q$, and $A$ are found to be comparable while those for $B$ and $p$
are relatively small.

A polynomial chaos surrogate model for the bulk thermal conductivity (observable)
as a function of SW potential
parameters at the bulk temperature of 300~K is constructed. The surrogate helps reduce the
computational effort required for forward propagation of the uncertainty from
parameters to the observable as well as for estimating the Sobol\textquotesingle~sensitivity indices.
Furthermore, the surrogate could be used to accelerate parameter calibration in a
Bayesian setting. However, since the surrogate relies on NEMD predictions, the
underlying computational effort is nevertheless significantly large. To circumvent
this challenge, we exploit our initial findings based on DGSM and construct
a reduced-order surrogate in 5 dimensions by fixing the parameters, $B$ and $p$.
We verify its accuracy by estimating the relative
L-2 norm of the error between NEMD predictions in the full space and the reduced-order
surrogate predictions, and by comparing the probability density of the
bulk thermal conductivity in Figure~\ref{fig:verify}. Furthermore, our initial
sensitivity trends based on DGSM-analysis using 25 samples seem to agree favorably
with Sobol\textquotesingle~sensitivity analysis based on 10$^{6}$ samples. Hence, it can be said
that DGSM-based analysis with a few samples could offer huge computational gains
by reliably reducing the dimensionality of a surrogate for uncertainty analysis.

Finally, we highlight key aspects of parameter calibration in a Bayesian setting.
The underlying motivation stems from the fact that the nominal estimates of the SW
parameters did not consider measurement error, simulation noise, model form error,
and parametric uncertainties. Calibration in a Bayesian framework allows us to
incorporate such errors and uncertainties in an efficient manner and provides
a joint posterior distribution of the uncertain parameters. To minimize computational
costs pertaining to the calibration process, we suggest the following sequence of
steps: First, perform DGSM analysis to 
identify parameters that are not so important. Second, construct a reduced-order
surrogate based on DGSM-analysis and verify its accuracy. Third, compute the
Sobol\textquotesingle~sensitivity indices using the surrogate to identify parameters for calibration. 
Fourth, construct a second surrogate in the reduced subspace described by the
calibration parameters, and quantify the surrogate error to be accounted for
in calibration. Fifth, evaluate the joint posterior using an efficient MCMC-based algorithm
such as adaptive Metropolis~\cite{Haario:2001} and its variants~\cite{Haario:2006, Green:2001}.

It is important to note that the strategies presented 
in this work are not restricted to a Si bar and the Stillinger-Weber potential, and
could be extended to a wide range of applications and inter-atomic potentials for
the purpose of uncertainty quantification.

### 2018-07-05 Paper/intro.tex
..

2. One approach to NEMD is the Direct Method, commonly used for estimating the bulk
thermal conductivity. A brief discussion on the direct method and associated pros and cons
(notes from Dellan's paper and book suggested by Amuthan) 
Predictions impacted by the choice of potential, values of
individual parameters, size, and potentially due to duration and applied thermal gradients
(cite Amuthan book, Francesco's paper, McGaughey's paper). 
Errors are introduced by thermostatting (Amuthan book). Nominal value of SW potential parameters
based on fitting against experiments and to ensure structural stability etc. (SW paper)

@@

Although widely used, the direct method is known to severely under-predict
the bulk thermal conductivity compared to experimental 
measurements~\cite{Haynes:2014,Shanks:1963}. This is primarily
due to length scales used in the simulation that are several orders of magnitude smaller
than those used in an experiment. As a result, the sample length is much smaller than the
bulk phonon mean free path leading to the so-called ballistic transport of the phonons.
The mean free path of such phonon modes is limited to the system size that reduces their
contribution to thermal transport. Moreover, the
introduction of thermostats typically reduces the correlation between vibrations of 
different atoms potentially reducing the thermal conductivity
further~\cite{Evans:2008}. Estimation of thermal conductivity using the
direct method is therefore impacted by the choice of system size and potentially due to
fluctuations in the thermal gradient experienced by the system due to thermostatting.

Predictions of non-equilibrium molecular dynamics (NEMD) simulations are also dependent on the
choice of the inter-atomic potential as well as values associated with individual parameters
of a given potential. For instance, in the case of crystalline Si, the Stillinger-Weber (SW)
inter-atomic potential is widely used. However, as discussed by Stillinger and Weber
in~\cite{Stillinger:1985}, their proposed nominal values of individual parameters were based
on a limited search in a 7D parameter space while ensuring structural stability and
reasonable agreement with experiments. It is therefore likely that these nominal estimates
for individual parameter values in the SW potential may not yield accurate results for a
wide variety of Si-based systems and warrant further investigation to study the impact of
underlying uncertainties on MD predictions. Along these lines, 
a recent study by Rizzi et al. focused on the effect of
uncertainties associated with the force-field parameters on bulk water properties using MD
simulations~\cite{Rizzi:2012}. Marepalli et al. in~\cite{Marepalli:2014} considered a stochastic model
for thermal conductivity to account for inherent noise in MD simulations, and study its impact on
spatial temperature 
distribution during heat conduction. Jacobson et al. in~\cite{Jacobson:2014} implemented an uncertainty
quantification framework to optimize a coarse-grained model for predicting the properties of monoatomic
 water. While these are significant contributions, it is only recently 
that researchers have started accounting for the presence of uncertainties in MD predictions in a
systematic manner. There is a definite need for additional efforts aimed at efficiency and accuracy
to enable uncertainty analysis in MD simulations for a wide range of applications.

In the present work, we focus our efforts on uncertainty analysis in the predictions of NEMD simulations
for phonon transport using a silicon bar. An overview of the set-up for the simulations is
provided in Section~\ref{sec:setup}. As discussed earlier, predictions from NEMD
exhibit large discrepancies with experimental observations depending upon system size and potentially
due to fluctuations in the applied thermal gradient. Additionally, the thermal conductivity estimates are
tightly coupled with parameter values associated with the inter-atomic potential. Hence, we set out to
accomplish multiple objectives through this research effort: First, we construct response surfaces
in order to characterize the dependence of discrepancy in thermal conductivity estimates (between
MD simulations and experiments) on system size, and applied thermal gradient~(Section~\ref{sec:response}).
Second, we perform sensitivity analysis to study the impact of SW potential parameter values on 
uncertainty in the predictions~(Section~\ref{sec:sense}).
Third, we exploit our findings from sensitivity analysis to 
construct a reduced order surrogate for uncertainty analysis~(Section~\ref{sec:ros}). 
Fourth, we illustrate the calibration
of important parameters in a Bayesian setting to evaluate their posterior
distributions~(Section~\ref{sec:bayes}). Construction of the
response surfaces, parametric sensitivity analysis, and Bayesian calibration can all be computationally
challenging endeavors especially in situations involving compute-intensive simulations as in the
case of NEMD. We therefore employ polynomial chaos (PC) surrogates~\cite{Xiu:2002,Ghanem:1990}
using non-intrusive spectral approaches~\cite{Olivier:2010} to reduce the computational effort pertaining
to the aforementioned objectives. Moreover, since the construction of a PC surrogate itself can be
expensive, we demonstrate a novel approach in Section~\ref{sec:sense} that implements derivative-based
sensitivity measures~\cite{Sobol:2010} to reduce the dimensionality of the surrogate a priori while
ensuring reasonable predictive accuracy.

>>>>

2. One approach to NEMD is the Direct Method, commonly used for estimating the bulk
thermal conductivity. A brief discussion on the direct method and associated pros and cons
(notes from Dellan's paper and book suggested by Amuthan) 
Predictions impacted by the choice of potential, values of
individual parameters, size, and potentially due to duration and applied temperature gradients
(cite Amuthan book, Francesco's paper, McGaughey's paper). 
Errors are introduced by thermostatting (Amuthan book). Nominal value of SW potential parameters
based on fitting against experiments and to ensure structural stability etc. (SW paper)

@@

Although widely used, the direct method is known to severely under-predict
the bulk thermal conductivity compared to experimental 
measurements~\cite{Haynes:2014,Shanks:1963}. This is primarily
due to length scales used in the simulation that are several orders of magnitude smaller
than those used in an experiment. As a result, the sample length is much smaller than the
bulk phonon mean free path leading to the so-called ballistic transport of the phonons.
The mean free path of such phonon modes is limited to the system size that reduces their
contribution to thermal transport. Moreover, the
introduction of thermostats typically reduces the correlation between vibrations of 
different atoms potentially reducing the thermal conductivity
further~\cite{Evans:2008}. \rev{The average temperature gradient experienced by the 
system could thus be different from the simulation input and is a potential source of 
uncertainty.} Estimation of thermal conductivity using the
direct method is therefore impacted by the choice of system size and potentially due to
fluctuations in the temperature gradient experienced by the system due to thermostatting.

Predictions of non-equilibrium molecular dynamics (NEMD) simulations are also dependent on the
choice of the inter-atomic potential as well as values associated with individual parameters
of a given potential. For instance, in the case of crystalline Si, the Stillinger-Weber (SW)
inter-atomic potential is widely used. However, as discussed by Stillinger and Weber
in~\cite{Stillinger:1985}, their proposed nominal values of individual parameters were based
on a limited search in a 7D parameter space while ensuring structural stability and
reasonable agreement with experiments. It is therefore likely that these nominal estimates
for individual parameter values in the SW potential may not yield accurate results for a
wide variety of Si-based systems and warrant further investigation to study the impact of
underlying uncertainties on MD predictions. \rev{Along these lines, 
a recent study by Wang et al. performed uncertainty quantification of thermal conductivities
from equilibrium molecular dynamics simulations~\cite{Wang:2017}}.
Rizzi et al. focused on the effect of
uncertainties associated with the force-field parameters on bulk water properties using MD
simulations~\cite{Rizzi:2012}. Marepalli et al. in~\cite{Marepalli:2014} considered a stochastic model
for thermal conductivity to account for inherent noise in MD simulations, and study its impact on
spatial temperature 
distribution during heat conduction. Jacobson et al. in~\cite{Jacobson:2014} implemented an uncertainty
quantification framework to optimize a coarse-grained model for predicting the properties of monoatomic
 water. While these are significant contributions, it is only recently 
that researchers have started accounting for the presence of uncertainties in MD predictions in a
systematic manner. There is a definite need for additional efforts aimed at efficiency and accuracy
to enable uncertainty analysis in MD simulations for a wide range of applications.

In the present work, we focus our efforts on uncertainty analysis in the predictions of NEMD simulations
for phonon transport using a silicon bar. An overview of the set-up for the simulations is
provided in Section~\ref{sec:setup}. As discussed earlier, predictions from NEMD
exhibit large discrepancies with experimental observations depending upon system size and potentially
due to fluctuations in the applied temperature gradient. Additionally, the thermal conductivity estimates are
tightly coupled with parameter values associated with the inter-atomic potential. Hence, we set out to
accomplish multiple objectives through this research effort: First, we construct response surfaces
in order to characterize the dependence of discrepancy in thermal conductivity estimates (between
MD simulations and experiments) on system size, and applied temperature gradient~(Section~\ref{sec:response}).
Second, we perform sensitivity analysis to study the impact of SW potential parameter values on 
uncertainty in the predictions~(Section~\ref{sec:sense}).
Third, we exploit our findings from sensitivity analysis to 
construct a reduced order surrogate for uncertainty analysis~(Section~\ref{sec:ros}). 
Fourth, we illustrate the calibration
of important parameters in a Bayesian setting to evaluate their posterior
distributions~(Section~\ref{sec:bayes}). Construction of the
response surfaces, parametric sensitivity analysis, and Bayesian calibration can all be computationally
challenging endeavors especially in situations involving compute-intensive simulations as in the
case of NEMD. We therefore employ polynomial chaos (PC) surrogates~\cite{Xiu:2002,Ghanem:1990}
using non-intrusive spectral approaches~\cite{Olivier:2010} to reduce the computational effort pertaining
to the aforementioned objectives. Moreover, since the construction of a PC surrogate itself can be
expensive, we demonstrate a novel approach in Section~\ref{sec:sense} that implements derivative-based
sensitivity measures~\cite{Sobol:2010} to reduce the dimensionality of the surrogate a priori while
ensuring reasonable predictive accuracy.

### 2018-07-05 Paper/sense.tex
..

We aim to compute the derivative-based sensitivity measure (DGSM) and hence the corresponding upper bound on the
Sobol\textquotesingle~total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
introduce small perturbations~($\mathcal{O}(10^{-5})n_i$; $n_i$ being the nominal value) to the nominal values
associated with each parameter and estimate the partial derivatives in Eq.~\ref{eq:mu} using finite difference. 
Hence, in order to compute $\mu_i$ using $N$ points in the d-dimensional parameter space, we require $N(d+1)$
model realizations. The SW potential parameters are considered to be uniformly distributed in a small interval
around the nominal value in which case $\mathcal{C}_i$ is given as $(u-l)^{2}/\pi^2$~\cite{Roustant:2014}; $u$
and $l$ being the upper and lower bounds of the interval respectively.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.65\textwidth]{./Figures/ub}
\caption{The quantity $\hat{\mathcal{C}_i\mu_i}$ as computed after 4 iterations and data at 200
points is plotted for each SW potential parameter.}
\label{fig:ub}
\end{center}
\end{figure}

>>>>

We aim to compute the DGSM and hence the corresponding upper bound on the
Sobol\textquotesingle~total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
introduce small perturbations~($\mathcal{O}(10^{-5})n_i$; $n_i$ being the nominal value) to the nominal values
associated with each parameter and estimate the partial derivatives in Eq.~\ref{eq:mu} using finite difference. 
Hence, in order to compute $\mu_i$ using $N$ points in the d-dimensional parameter space, we require $N(d+1)$
model realizations. The SW potential parameters are considered to be uniformly distributed in a small interval
around the nominal value in which case $\mathcal{C}_i$ is given as $(u-l)^{2}/\pi^2$~\cite{Roustant:2014}; $u$
and $l$ being the upper and lower bounds of the interval respectively.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.5\textwidth]{./Figures/ub}
\caption{The quantity $\hat{\mathcal{C}_i\mu_i}$ as computed after 4 iterations and data at 200
points is plotted for each SW potential parameter.}
\label{fig:ub}
\end{center}
\end{figure}

### 2018-07-05 Paper/setup.tex
..

In this work, non-equilibrium molecular dynamics (NEMD) simulations are performed using the 
LAMMPS~\cite{Plimpton:2007} software package.
Essentially, a thermal gradient is applied by means of \rev{Langevin} thermostats located
at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
as shown using a schematic in Figure~\ref{fig:setup}.

\begin{figure}[htbp]
\begin{center}
\begin{tabular}{cc}
  \includegraphics[width=0.48\textwidth]{./Figures/schematic}
  &
  \hspace{3mm}
  \includegraphics[width=0.40\textwidth]{./Figures/Sibar_05}
  \\ (a) & (b)
  \end{tabular}
\caption{(a) Schematic illustration of the set-up for evaluating thermal conductivity of Si using NEMD. (b) 
Arrangement of Si atoms prior to the application of thermal gradient.}
\label{fig:setup}
\end{center}
\end{figure}

The set of
inputs to LAMMPS is provided below in Table~\ref{tab:input}. Note that specific values for the length of the bar
and the applied thermal gradient are not provided since we investigate thermal conductivity trends for a range of 
values of the two parameters as discussed later in Section~\ref{sec:response}. A careful analysis focused on
minimizing temperature fluctuations during different stages of the simulation was performed to optimize for the
choice of height and width of the bar as well as the duration of the simulation.

@@

\be
 \kappa = \frac{q}{\left|\frac{dT}{dz}\right|} 
\ee

\noindent where $\left|\frac{dT}{dz}\right|$ denotes the magnitude of the applied temperature gradient along the 
direction of heat flow (see~Figure~\ref{fig:setup}(a)).

>>>>

In this work, non-equilibrium molecular dynamics (NEMD) simulations are performed using the 
LAMMPS~\cite{Plimpton:2007} software package.
Essentially, a temperature gradient is applied by means of \rev{Langevin} thermostats located
at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
as shown using a schematic in Figure~\ref{fig:setup}.

\begin{figure}[htbp]
\begin{center}
\begin{tabular}{cc}
  \includegraphics[width=0.48\textwidth]{./Figures/schematic}
  &
  \hspace{3mm}
  \includegraphics[width=0.40\textwidth]{./Figures/Sibar_05}
  \\ (a) & (b)
  \end{tabular}
\caption{(a) Schematic illustration of the set-up for evaluating thermal conductivity of Si using NEMD. (b) 
Arrangement of Si atoms prior to the application of temperature gradient.}
\label{fig:setup}
\end{center}
\end{figure}

The set of
inputs to LAMMPS is provided below in Table~\ref{tab:input}. Note that specific values for the length of the bar
and the applied temperature gradient are not provided since we investigate thermal conductivity trends for a range of 
values of the two parameters as discussed later in Section~\ref{sec:response}. A careful analysis focused on
minimizing temperature fluctuations during different stages of the simulation was performed to optimize for the
choice of height and width of the bar as well as the duration of the simulation.

@@

\be
 \kappa = \frac{\rev{q''}}{\left|\frac{dT}{dz}\right|} 
\ee

\noindent where \rev{$q''$ denotes the steady state heat flux (W/m$^2$)} and
$\left|\frac{dT}{dz}\right|$ denotes the magnitude of the applied 
temperature gradient along the direction of heat flow (see~Figure~\ref{fig:setup}(a)).
